Flatiron cleaning

### 2021-10-21 Rmd/rdi analysis adjusted weight.Rmd
report with adjusted weight

# `r emo::ji("spiral_notepad")` This report is using **actual weight**

@@

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

@@

  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

@@

           bmi_at_dx, bmi_cat, 
           weight_at_dx, height_at_dx, bsa_at_dx,

@@

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat",

@@

## 2.Clinical Plots
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

@@

Taxanes
```{r Table4 summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

>>>>

# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**

```{r echo=TRUE}
# # Calculate ideal dody weight
#   mutate(ideal_weight = case_when(
#     height <= 1.524               ~ 45.5 + 2.3,
#     height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
#   )) %>% 
#   mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
#   ) %>% 
#   mutate(actual_bmi = weight / (height * height)) %>%
#   mutate(actual_bmi_cat = case_when(
#     actual_bmi < 25                    ~ "Underweight and normal weight",
#     actual_bmi >= 25 &
#       actual_bmi < 30                  ~ "Overweight",
#     actual_bmi >= 30                   ~ "Obese"
#   )) %>%
#   mutate(actual_bmi_cat = factor(actual_bmi_cat, 
#                                   levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
#   # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
#   # Calculate CrCl
#   inner_join(., clinical_data %>% select(-surgerydate),
#              by = "patientid") %>% 
#   mutate(CrCl = (
#        (
#     ((140 - ageatdx) * weight) /
#     (72 * creatinine)
#        ) *
#     0.85)
#   ) %>% 
#   mutate(CrCl = case_when(
#     CrCl > 125                        ~ 125,
#     TRUE                              ~ CrCl
#   )) %>% 
#   mutate(adjusted_CrCl = case_when(
#     actual_bmi >= 25                  ~ CrCl,
#     actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
#   )) %>% 
#   mutate(adjusted_CrCl = case_when(
#     adjusted_CrCl > 125               ~ 125,
#     TRUE                              ~ adjusted_CrCl
#   )) 
```

@@

$$CrCl = \frac{(140 - ageatdx) * adjusted_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

@@

  mutate(relative_dose_intensity = amount / adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

@@

           actual_bmi, actual_bmi_cat, 
           weight_at_dx, height_at_dx, bsa_at_dx,

@@

           actual_bmi, actual_bmi_cat, "BSA",
           "stagecat",

@@

## 2.Clinical Plots
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= actual_bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = actual_bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

@@

# OS by actual_bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ actual_bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

# OS by actual_bmi_cat
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ actual_bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
Platin  
```{r Table4 summary Platin}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

@@

Taxanes
```{r Table4 summary Taxanes}
tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              type = list(mean_RDI_per_drug ~ 'continuous'),
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl8 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
  tbl_summary(by = actual_bmi_cat,
              label = list(mean_RDI_per_drug ~ "RDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl9 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
